\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}

\title{\vspace{-4cm}Resume}
\date{}

\begin{document}

\maketitle

\noindent
\textbf{Alexander von Stuelpnagel}\\
Chicago, Illinois, United States\\
\texttt{avons394@gmail.com | 3236466099}\\
\texttt{linkedin.com/in/alexander-von-stuelpnagel-a20386156}

\section*{Summary}

Experienced full-stack Java developer with a robust understanding of both relational and NoSQL databases, as well as familiarity with REST APIs and GraphQL. As a Computer Science graduate, my skill set bridges the gap between technology and business, facilitating cross-functional collaboration throughout the product lifecycle. I thrive on complex challenges and constantly seek opportunities to fine-tune performance and enhance user experience.

\section*{Experience}

\noindent
\textbf{Full Stack Engineer}\\
\textit{Ford Motor Company, Aug 2022 - Present (10 months)}
\begin{itemize}[noitemsep]
    \item Involved in the development and maintenance of various consumer-facing applications.
    \item Experimented with GraphQL in a proof-of-concept to streamline data query processes.
    \item Actively involved in initiatives to optimize application performance and efficiency.
\end{itemize}

\noindent
\textbf{Software Consultant}\\
\textit{Accenture, Aug 2019 - Jul 2021 (2 years)}
\begin{itemize}[noitemsep]
    \item Participated in several projects revolving around claims tracking and event stream configuration for a Fortune 500 healthcare company.
    \item Played a key role in brainstorming and conceptualizing a potential shift from a traditional health claim API to a more efficient GraphQL-based solution.
    \item Collaborated with teams in navigating the complexities of an event streaming architecture.
\end{itemize}

\noindent
\textbf{Full Stack Developer}\\
\textit{Revature, May 2018 - Jul 2018 (3 months)}

\section*{Education}
\noindent
\textbf{University of Vermont}\\
\textit{2013 - 2017 (4 years)}\\
BSc in Computer Science, minor in Business Administration

\section*{Skills}
Git • Java • SQL • JavaScript • C • C++ • Spring Framework • Amazon Web Services (AWS) • Microservices • Communication • NoSQL • REST APIs • GraphQL • Performance Tuning • Familiarity with Kafka

\end{document}
